clusters

### 2015-07-09 cluster.rmd
10 clusters

qqPlot(all7c$suc,
       main='success')

qqPlot((all7c$suc+102700) %>% log)

@@

ggplot(all7c, aes_string(x='suc')) + geom_histogram(aes(y=..density..))

@@

trial<- (all7c$suc) %>% as.data.frame
ggplot(trial, aes_string(x='.')) + geom_histogram(aes(y=..density..))

### CAN WE TAKE LOG OF ABSOLUTE VALUES AND THEN MAKE NUMBERS THAT WERE PREVIOUSLY NEG NEG AGAIN?

clust$suc<- scale(all7c$suc)

@@

Repeat clustering with new suc

@@

clust.km<- cascadeKM(clust %>% select(inv.mlsto, balance.mlsto, return.pdol,
                                      suc, pc.pro, hrs.mlsto
                                      ), 2, 20, iter= 100)
plot(clust.km, sortg = TRUE, grpmts.plot = TRUE)

# 10 clusters
# Cluster cohesion: create plots of SSE index (distance within clusters - sum of squared error) 
# then calinksi (index of cluster homogeneity and distance where higher number is better)
# calinski: between cluster distance/within cluster distance
ind.plot<- melt(clust2.km$results)
ggplot(ind.plot %>% filter(Var1 == 'SSE'), aes(x=Var2, y=value, group=1)) + 
        geom_line( ) +
        theme(axis.text.x=element_text(angle=45,hjust=1))
ggplot(ind.plot %>% filter(Var1 == 'calinski'), aes(x=Var2, y=value, group=1)) + 
        geom_line( )+
        theme(axis.text.x=element_text(angle=45,hjust=1))
# 17 clusters should be good
```

>>>>

qqPlot(all7c$return.pdol,
       main='success')

qqPlot(sapply(all7c$suc, function(x){sign(x)*log(abs(x) + 1)}))
qqPlot((all7c$suc) %>% math.cbrt)

@@

ggplot(all7c, aes_string(x='inv.vs.cost')) + geom_histogram(aes(y=..density..))

@@

trial<- (sapply(all7c$suc, function(x){sign(x)*log(abs(x) + 1)})) %>% as.data.frame
colnames(trial)[names(trial) %in% '.']<-'var'
ggplot(trial, aes_string(x='var')) + geom_histogram(aes(y=..density..))
skewness(trial$var)
kurtosis(trial$var)
mean(trial$var)
sd(trial$var)
trial$scale.var<- scale(trial$var)
ggplot(trial, aes_string(x='scale.var')) + geom_histogram(aes(y=..density..))
# ggplot still looks bimodal after scaling

## conclusion - lets take neglog of suc and scale it, add it to clust

clust$suc<- sapply(all7c$suc, function(x){sign(x)*log(abs(x) + 1)}) %>% scale()

## should we make return.pdol bimodal??
math.cbrt <- function(x) {
        sign(x) * abs(x)^(1/3)
}
qqPlot(all7c$return.pdol %>% math.cbrt,
       main='success')
trial<- (all7c$return.pdol %>% math.cbrt) %>% as.data.frame
colnames(trial)[names(trial) %in% '.']<-'var'
ggplot(trial, aes_string(x='var')) + geom_histogram(aes(y=..density..))
skewness(trial$var)
kurtosis(trial$var)
trial$scale.var<- scale(trial$var)
ggplot(trial, aes_string(x='scale.var')) + geom_histogram(aes(y=..density..))
#take cube root of return.pdol and scale it to clust

clust$return.pdol<- all7c$return.pdol %>% math.cbrt %>% scale()

@@

Repeat clustering with new suc and revised bi-modal return.pdol

@@

clust.km<- cascadeKM(clust %>% select(inv.mlsto, balance.mlsto, return.pdol,
                                      suc, hrs.mlsto), 2, 15, iter= 100)
plot(clust.km, sortg = TRUE, grpmts.plot = TRUE)

# 10 clusters
# Cluster cohesion: create plots of SSE index (distance within clusters - sum of squared error) 
# then calinksi (index of cluster homogeneity and distance where higher number is better)
# calinski: between cluster distance/within cluster distance
ind.plot<- melt(clust2.km$results)
ggplot(ind.plot %>% filter(Var1 == 'SSE'), aes(x=Var2, y=value, group=1)) + 
        geom_line( ) +
        theme(axis.text.x=element_text(angle=45,hjust=1))
ggplot(ind.plot %>% filter(Var1 == 'calinski'), aes(x=Var2, y=value, group=1)) + 
        geom_line( )+
        theme(axis.text.x=element_text(angle=45,hjust=1))

# 10 clusters should be good

# have a look at dendrogram with 10 clusters

x<- dist(clust %>% select(inv.mlsto, balance.mlsto, return.pdol, suc, hrs.mlsto), 
         method = 'euclidean')
fit<- hclust(x, method = 'ward.D2')
plot(fit)

rect.hclust(fit, k=10, border='red')

#looks good!

now want 10 clusters, based on k means optimisation, have a look at average characteristics

k1<- kmeans(clust %>% select(inv.mlsto, balance.mlsto, return.pdol, suc, hrs.mlsto), 10)

all7c$groups<- k1$cluster
kmeans.plot<- all7c %>% select(inv.mlsto, timespan, no.users, pc.pro, client.totinv,
                         Num.disc, Num.days, mean.peeps, hours.perday, balance.mlsto, hrs.mlsto,
                         cost.mlsto, return.pdol, suc, groups)
all7c.plot<- ddply(kmeans.plot, .(groups), numcolwise(mean))
all7c.plot$groups<- rownames(all7c.plot)
k2.melt<- melt(all7c.plot)

#summary means of all numeric variables in 5 clusters
clust.summary<- all7c.plot %>% select(-groups) %>% round(2)
tab<- table(all7c$groups) %>% prop.table %>% as.data.frame
bal<- sum(all7c$balance.mlsto)
hrs<-  sum(all7c$hrs.mlsto)
clust.summary$pc.jobs<- round( tab[,2]*100, 1)
clust.summary$bal.pc<- ddply(all7c, .(groups), summarise, bal.pc= round(sum(balance.mlsto)/bal*100, 1)) %>% 
        select(2)
clust.summary$hrs.pc<- ddply(all7c, .(groups), summarise, hrs.pc= round(sum(hrs.mlsto)/hrs*100, 1)) %>% 
        select(2)
clust.summary$job.count<- table(all7c$groups) %>% as.data.frame %>% select(Freq)

clust.summary<- clust.summary %>% select(inv.mlsto, suc, return.pdol, cost.mlsto, balance.mlsto, hrs.mlsto, hours.perday, timespan, Num.days, Num.disc, no.users, pc.pro, mean.peeps, client.totinv, pc.jobs, bal.pc, hrs.pc)

all7c.med<- all7c.med %>% select(inv.mlsto, suc, return.pdol, cost.mlsto, balance.mlsto, hrs.mlsto, hours.perday, timespan, Num.days, Num.disc, no.users, pc.pro, mean.peeps, client.totinv)
